\job
{2020} {Present}
{Meta (Facebook) Integrity} {https://about.fb.com/news/category/integrity-security/}
{Software Engineer Level 5}
{
    Embedded in Meta's Integrity organization, which keeps users safe from harm (think spam, illicit content, criminal activity, and much more) across the company's many platforms, I help my team align the wide range of integrity teams on standardized practices to protect user privacy. As tech lead on my team, I drive discussions with partner teams across the company, proposing and aligning processes, designing solutions, and leveraging teammates to help design and implement subprojects. The work I have done has provided data and influence on the \coloredlink {https://hacklang.org} {Hack language}, reduced load on Integrity teams in response to \coloredlink {https://about.fb.com/news/category/data-and-privacy} {privacy regulations and commitments}.
}

\job
{2018} {2020}
{Prime Video} {https://www.amazon.com/b?node=17020161011}
{Software Development Engineer II-III}
{
    For the Living Room Infrastructure and Tooling team, I lead my team in the development of backend services and a tooling ecosystem for developer productivity for the Prime Video application on devices ranging from low-end smart TVs and streaming sticks to gaming consoles. This includes designing and implementing multi-service orchestrations for developer productivity while ensuring the stability and security of the application for customers.
}

\job
{2017} {2018}
{AWS WorkLink} {https://aws.amazon.com/worklink}
{Software Development Engineer II}
{
    Joining right at the conception of the AWS WorkLink service, I lead feature investigations and architecture designs, and built critical components of the service's control plane. In this role, I developed skills in API design, service availability, and networking primitives.
}

\job
{2016} {2017}
{Amazon Shopping App} {https://amazon.com/mobileapps}
{Software Development Engineer II}
{
    On this platform-development team for the shopping app, I investigated and upgraded hundreds of code repositories and build tools to the latest version of \coloredlink {https://gradle.org} {Gradle} and the \coloredlink {https://developer.android.com/studio/build/index.html} {Android Gradle Plugin}. This involved deep investigations on conventions and implementation details, resulting in a rich understanding of how Gradle and Android Gradle builds work.
}

\job
{2014} {2016}
{AWS Silk} {https://docs.aws.amazon.com/silk}
{Software Development Engineer I-II}
{
    Designed and built customer-facing features for the Silk browser that are viewed millions of times a day.
}

\job
{2013} {}
{Amazon.com} {https://amazon.com}
{Software Development Engineer Intern}
{
    Designed and implemented a service for receiving and storing activity metrics for internal tools.
}
