\personalProject {https://github.com/quittle/wowser} {Wowser} {Rust} {
    I decided to learn \coloredlink {https://www.rust-lang.org/} {Rust} while also diving deep into the fundamentals of how browsers work. I started from scratch in order to learn, building nearly everything myself: font parsing, HTTP client, a generic language parsing framework for HTML, CSS, and Javascript, a layout and rendering engine that leverages these languages.
}

\personalProject {https://github.com/quittle/a11y-ally} {A11y Ally} {Android,Kotlin} {
    An Android application for developers that allows them to detect accessibility issues in their own apps and, overall, gain insight into the experiences of users that are dependent on assistive technologies. As part of this effort I reached out to accessibility professionals like \coloredlink {https://www.deque.com} {Deque} to learn from them and share my experience and ideas.
}

\personalProject {} {Bazel Build System Libraries} {Skylark,Python,Java} {
    \begin {minimalItemize}
        \item \href {https://github.com/quittle/bazel_travis_toolbox} {Bazel Travis Toolbox} \spaceemdash Minimal support library for building Bazel projects on Travis CI\@.
        \item \href {https://github.com/quittle/bazel_repository_toolbox} {Bazel Repository Toolbox} \spaceemdash Repository rules for simpler integration into common code repositories while encouraging best practices.
        \item \href {https://github.com/quittle/bazel_toolbox} {Bazel Toolbox} \spaceemdash Enables simpler Bazel rule development and testing as a library of common rules, actions, and macros.
        \item \href {https://github.com/quittle/rules_web} {Bazel Web Rules} \spaceemdash An opinionated collection of rules for building websites in Bazel.
    \end {minimalItemize}
}

\personalProject {https://github.com/quittle/ahoy} {Ahoy: The Friendly C++ Arrrg Parser} {C++} {
    A C++ argument parser utilizing template meta-programming to build an argument parser that avoids macros and ensures compile-time correctness of parameter configuration.
}

\personalProject {https://github.com/quittle/www_dramaticzoom_com} {Dramatic Zoom} {HTML,CSS,JS,PHP,MySQL} {
    An image sharing site with a twist: the images \coloredlink {https://youtu.be/y8Kyi0WNg40} {zoom in while playing dramatic music}. This used to be an operational site I ran but have since taken it down.
}

\personalProject {https://github.com/quittle/rules_web/blob/master/fonts/scripts/minify_ttx.py} {TTF Minifier} {Python} {
    Parses True-Type Font files using \coloredlink {https://github.com/fonttools/fonttools} {FontTools}, prunes unnecessary tables and entities, and renames glyphs for brevity.
}

\personalProject {https://fallingsand.dustintoff.com} {Falling Sand Game} {HTML5,JS} {
    A \href {https://en.wikipedia.org/wiki/Falling-sand_game} {traditional implementation} where players can draw various elements (sand, water, plant, etc.) in a 2D world to interact with each other with a crude, hand-written, physics engine.
}

\personalProject {} {Boot Animation Shuffle} {Android/PHP} {
    Imports and generates boot animations for Android devices. Includes an animation gallery where users can upload and share animations with other users.
}

More projects available on {\coloredlink {https://github.com/quittle} {my GitHub}} and {\coloredlink {https://dustintoff.com/\#projects} {dustintoff.com}}.